\papertitle

### 2014-03-20 final-report/paper.tex

\todo{write me}

>>>>

The Worker Communication view consists of two charts: the aggregate communication 
chart and the time series chart. The aggregate communication chart is a matrix representing
a cluster of $N$ workers. Each cell $m,n$ in the matrix represents the total number of tuples sent
by worker $m$ to worker $n$ during the query execution. Figure \ref{fig:matrix} shows this chart along 
with the selected link in the query plan DAG.

\begin{figure}[ht]
  \includegraphics[width=\columnwidth]{images/networkVis1}
  \caption{Worker communication matrix chart.}
  \label{fig:matrix}
\end{figure}
